### 2024-11-16 paper/1-intro.tex
Add SpecTec and problem in intro

% SpecTec
To alleviate this problem, we had been developing SpecTec, a framework for
mechanizing WebAssembly specification.
It provides DSL to define Wasm syntax and semantics in a declarative style
similar to the formal notation.
It type-checks DSL to prevent meta-level specification errors, and generates
many artifacts including the specification document, a Wasm interpreter, and
mechanized definitions for theorem provers.

% AL
To express

% problem
However, AL cannot describe Wasm control flow correctly

>>>>

% SpecTec
To mitigate this problem, we \red{had been} developing SpecTec, a framework for
mechanizing WebAssembly specification.
It provides domain specific language (DSL) that enables the declarative
definition of Wasm syntax and semantics, akin to the formal notation.
Additionally, to capture the pseudocode-like structure of the prose notation,
SpecTec incorporates an imperative language, \textit{AL}.
SpecTec performs type-checking on the DSL to prevent meta-level specification
errors, translates the DSL into AL, and generates various artifacts, including
the specification document, a Wasm interpreter, and mechanized definitions for
theorem provers, along with the DSL and AL.
Notably, AL plays a central role in the generation of the Wasm interpreter,
bridging the gap between formal specification and executable code.

% problem
However, at that time, AL was unable to capture the Wasm control flow
correctly.
The Wasm interpreter generated using AL produced wrong results when running
Wasm official test suites.
Additionally, the lack of formal semantics or a formalized definition for AL
made it difficult to identify and address the fundamental issues in its design.
Since running tests is the primary method for assessing the correctness of the
specification, this limitation hindered the development of both the generated
interpreter and the specification itself.
This underscored the need for a more robust approach to formally define AL and
ensure its alignment with Wasm's complex semantics.
